Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2022-06-09 Writing/manuscript_gwr.rmd
update results with 3 price ratios: 25% (5.44), 50% (6.56), 75% (7.67)

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff]

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA. The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.

>>>>

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff] %>% 
  #only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>% 
  #=== label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>% 
  .[pRatio==5.44, pLabel := "Low"] %>%
  .[pRatio==6.56, pLabel := "Middle"] %>%
  .[pRatio==7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, the profit difference between the GWR-based VRA and the SCAM-based URA. Three price ratios (nitrogen fertilizer price $\$$ kg$^{-1}$ divided by corn price $\$$ kg$^{-1}$) were used in the simulations: 5.44 (low), 6.56 (medium), and 7.67 (high). The three price ratios were selected by taking the 25%, 50%, and 75% quantile of the historical monthly price ratios from the years 1990 to 2022, where the historical corn prices were collected from the USDA-NASS, and nitrogen fertilizer prices were collected from the DTN website. The price ratio represents the relative nitrogen fertilizer price to corn price. For Figure \@ref(fig:pi-dif-dist) results, the recent period (June 2022) corn price of about $\$$ 0.28kg$^{-1}$ was used, which are corresponding to absolute nitrogen fertilizer prices of $\$$ 0.69kg$^{-1}$ (low), $\$$ 0.83kg$^{-1}$ (medium), and $\$$ 1.31kg$^{-1}$ (high). Using other corn prices will change the absolute sizes of profit difference. But since the optimal nitrogen rate ($\hat{N}^*$) calculation is only affected by the relative nitrogen-to-corn price ratio, the changes in the absolute sizes of profit difference will be proportional to the values in Figure \@ref(fig:pi-dif-dist), and the distribution shapes will not be affected. For example, if corn price used is 10% lower, the profit differences will also be 10% lower.

*(The results part needs to be rewritten)*

The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.
